Recursive Solutions to First-Order Model Counting

### 2022-11-22 doc/paper/paper.tex
Small changes

\begin{example}\label{example:interpretation}
  Consider the FCG from \cref{fig:examplefcg}. The input formula (i.e., the
  formula from \cref{example:first}) has two domains: $\Gamma$ and $\Delta$.
  Thus, the interpretation of the FCG is a function
  $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
  $m \coloneqq |\Gamma|$, and $n \coloneqq |\Delta|$. The node labelled
  $\bigvee_{\Delta^{\top} \subseteq \Delta}$ tells us that
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
  interpretation of the remaining subgraph, and $l$ iterates over all possible
  sizes of $\Delta^{\top}$. It also creates two subdomains
  $\Delta^{\top}, \Delta^{\bot} \subseteq b$ that partition $\Delta$, i.e., as
  the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
  correspondingly decreases. Nodes labelled $\land$ correspond to
  multiplication. Therefore,
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
  where $\diamondsuit$ is the interpretation of the contradiction (i.e., $\bot$)
  node, and $\heartsuit$ is the interpretation of the $\Reff$ node.

>>>>

\begin{example}\label{example:interpretation}
  Consider the FCG from \cref{fig:examplefcg}. The input formula (i.e., the
  formula from \cref{example:first}) has two domains: $\Gamma$ and $\Delta$.
  Thus, the interpretation of the FCG is a function
  $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
  $m \coloneqq |\Gamma|$, and $n \coloneqq |\Delta|$. The node labelled
  $\bigvee_{\Delta^{\top} \subseteq \Delta}$ tells us that
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
  interpretation of the remaining subgraph, and $l$ iterates over all possible
  sizes of $\Delta^{\top}$. It also creates two subdomains
  $\Delta^{\top}, \Delta^{\bot} \subseteq \Delta$ that partition $\Delta$, i.e.,
  as the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
  correspondingly decreases. Nodes labelled $\land$ correspond to
  multiplication. Therefore,
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
  where $\diamondsuit$ is the interpretation of the contradiction (i.e., $\bot$)
  node, and $\heartsuit$ is the interpretation of the $\Reff$ node.
